### 2015-06-01 writing/SNLI paper/entailment_eval.tex
Last few style edits.

% Results
We report results in \reftab{tab:bowresults}, along with ablation studies for removing
  the cross-bigram features (leaving only the cross-unigram feature),
  and for removing all lexicalized features.
% Insights 1: lexicalization helps a bunch
On our large corpus in particular, there is a substantial jump in accuracy from using
  lexicalized features, and another from using the very sparse
  cross-bigram features.
The latter  result can be explained if
  the classifier automatically learns to recognize explicit negations and adjective
  modification, and a similar result was shown in
  \newcite{sidaw12simple} for bigram features in sentiment analysis.

@@

The results are shown in \reftab{tab:transferresults}. Training on SICK alone yields poor performance, and the model trained on our data misunderstands the subtly different meanings of the (identically named) SICK labels, labeling more \ii{neutral} examples as \ii{contradiction}s than correctly. Transferring representations, in contrast, yields the best performance yet reported on SICK for an unaugmented neural network model, surpasses the available EOP models, and approaches both the overall state of the art at 84.6\% \cite{lai2014illinois} and the 84\% level of interannotator agreement, which likely represents an approximate performance ceiling. This suggests that the introduction of a large high-quality corpus makes it  possible to train representation-learning models for sentence meaning that are competitive with the best hand-engineered models on inference tasks.

>>>>

% Results
We report results in \reftab{tab:bowresults}, along with ablation studies for removing
  the cross-bigram features (leaving only the cross-unigram feature)
  and for removing all lexicalized features.
% Insights 1: lexicalization helps a bunch
On our large corpus in particular, there is a substantial jump in accuracy from using
  lexicalized features, and another from using the very sparse
  cross-bigram features.
The latter  result can be explained if
  the classifier automatically learns to recognize explicit negations and adjective
  modification, and a similar result was shown in
  \newcite{sidaw12simple} for bigram features in sentiment analysis.

@@

The results are shown in \reftab{tab:transferresults}. Training on SICK alone yields poor performance, and the model trained on our data alone misunderstands the subtly different meanings of the (identically named) SICK labels, labeling more \ii{neutral} examples as \ii{contradiction}s than correctly. Transferring representations, in contrast, yields the best performance yet reported on SICK for an unaugmented neural network model, surpasses the available EOP models, and approaches both the overall state of the art at 84.6\% \cite{lai2014illinois} and the 84\% level of interannotator agreement, which likely represents an approximate performance ceiling. This suggests that the introduction of a large high-quality corpus makes it  possible to train representation-learning models for sentence meaning that are competitive with the best hand-engineered models on inference tasks.
